---
title: "background.rmd"
output: ioslides_presentation
date: "2022-10-04"
---

```{R}

```
What statistics are most predictive of NBA champions during the regular season over the last 5 years?

Does that data already exist? Can you get it?
- Based on our conversations in class and assignments that we've done, I would think that the data exists already. I can key in on a few particular data points and try to check that over time. But I do feel like that data exists and is accessible.
Do you need assistance in getting it?
- I think we used this data looking into the NBA once before, so that would be helpful to have a reminder where that is and if there is anything else I need to do to the data.
What time frame do you want/need data from?
- I would say I want the to analyze the last five NBA champions. However, if that is too ambitious I could do the last 3 years. If 5 years isn't that ambitious, then I could analyze the last decade.
Will you have to improve or augment the data in order to answer your question? If so, how?
- Based on our in class assignment, I do not initially think I will have to augment the data too much.
Are there other examples of this kind of work (specific or general)? If so, provide them.

https://www.cbssports.com/nfl/news/nfl-2022-stats-notes-and-nuggets-for-every-fan-to-remember-entering-week-1/
"Blowouts in the NFL, they matter. Here's why. Six of the last seven and seven of the last nine Super Bowl winners finished in the top 5 in point differential during the regular season. We had a nice streak rolling of top 5 point differential Super Bowl teams until last year's Rams took home the Lombardi Trophy and received those epic Super Bowl rings. 

But, hey, Los Angeles wasn't some obscure outlier. That team was sixth in point differential. And randomly cutting off at the top 5 because it's a round number is kind of silly, isn't it? How about the average point differential for Super Bowl winners? In the last six seasons, they've averaged a per-game point differential of 8.58 points, which equates to nearly +146 points in point differential during the regular season, which is between the Chiefs' and Buccaneers' point-differential number from a season ago."
^Something like this but I want to be more precise, using a collections of different statistics. 





## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

